# (PART) 概率論 Probability {-}

```{r probability-setup, include=FALSE}
# Ensure 'bugpath' exists when rendering this chapter standalone (outside index.Rmd)
if (!exists("bugpath", inherits = FALSE)) {
	bugpath <- getwd()
}
```

	
# 概率論入門：定義與公理 {#prob-intro}

> Statistics - A subject which most statisticians find difficult but which many physicians are experts on.
> ~ Stephen S. Senn

```{block2, note-thankElizabeth, type='rmdnote'}
The Probability lectures were orgainised and taught by Professor [Elizabeth Williamson](https://www.lshtm.ac.uk/aboutus/people/williamson.elizabeth).
```

```{r Prob-Session01, child = ('01-Probability/Session01.Rmd')}
```


# Bayes 貝葉斯理論的概念 {#Bayes-Definition}

```{r Prob-Session02, child = ('01-Probability/Session02.Rmd')}
```

# 期望 Expectation (或均值 or mean) 和 方差 Variance {#expectation}


```{r Prob-Session03, child = ('01-Probability/Session03.Rmd')}
```



# 伯努利分佈 Bernoulli distribution {#bernoulli}


```{r Prob-Session04, child = ('01-Probability/Session04.Rmd')}
```




# 二項分佈的概念 Binomial distribution {#binomial}


```{r Prob-Session05, child = ('01-Probability/Session05.Rmd')}
```



# 泊松分佈 Poisson Distribution {#poisson}


```{r Prob-Session06, child = ('01-Probability/Session06.Rmd')}
```


# 正（常）態分佈 Normal Distribution {#normaldistr}


```{r Prob-Session07, child = ('01-Probability/Session07.Rmd')}
```



# 中心極限定理  the Central Limit Theorem {#CLT}



```{r Prob-Session08, child = ('01-Probability/Session08.Rmd')}
```

