# (PART) 統計推斷 Inference {-}

# 統計推斷的概念 {#inference-basic}

> If people do not believe that mathematics is simple, it is only because they do not realize how complicated life is.
> ~ [John von Neumann](https://zh.wikipedia.org/wiki/%E7%BA%A6%E7%BF%B0%C2%B7%E5%86%AF%C2%B7%E8%AF%BA%E4%BC%8A%E6%9B%BC)

```{block2, note-thankDan, type='rmdnote'}
The Inference lectures were orgainised and taught by Professor [Daniel Altmann](https://www.lshtm.ac.uk/aboutus/people/altmann.daniel), Professor [John Gregson](https://www.lshtm.ac.uk/aboutus/people/gregson.john), and Dr. Katy Morgan.
```

```{r Infer-Session01, child = ('02-Inference/Session01.Rmd')}
```



# 估計和精確度 Estimation and Precision {#estimation-and-precision}

```{r Infer-Session02, child = ('02-Inference/Session02.Rmd')}
```


# 卡方分佈 Chi-square distribution {#chi-square-distribution}


```{r Infer-Session03, child = ('02-Inference/Session03.Rmd')}
```

# 似然 Likelihood {#likelihood-definition}

```{r Infer-Session04, child = ('02-Inference/Session04.Rmd')}
```



# 對數似然比 Log-likelihood ratio {#llr}


```{r Infer-Session05, child = ('02-Inference/Session05.Rmd')}
```


## Inference Practical 05 



```{r Infer-practical05, child = ('02-Inference/Practical05.Rmd')}
```


# 二次方程近似法求對數似然比  approximate log-likelihood ratios {#quadratic-llr}

```{r Infer-Session06, child = ('02-Inference/Session06.Rmd')}
```



## Inference Practical 06

```{r Infer-practical06, child = ('02-Inference/Practical06.Rmd')}
```


# 假設檢驗的構建 Construction of a hypothesis test {#hypothesis-test}


```{r Infer-Session07, child = ('02-Inference/Session07.Rmd')}
```



## Inference Practical 07

```{r Infer-practical07, child = ('02-Inference/Practical07.Rmd')}
```



# 假設檢驗的近似方法 {#approximation-hypo-test}


```{r Infer-Session08, child = ('02-Inference/Session08.Rmd')}
```

## Inference Practical 08

```{r Infer-practical08, child = ('02-Inference/Practical08.Rmd')}
```

# 正態誤差模型  Normal error models {#normal-error-models}


```{r Infer-Session09, child = ('02-Inference/Session09.Rmd')}
```


## Inference Practical 09

```{r Infer-practical09, child = ('02-Inference/Practical09.Rmd')}
```


# 多個參數時的統計推斷 Inference with multiple parameters I {#inference-with-multiple-para}


```{r Infer-Session10, child = ('02-Inference/Session10.Rmd')}
```


## Inference Practical 10

```{r Infer-practical10, child = ('02-Inference/Practical10.Rmd')}
```


# 多個參數時的統計推斷 -- 子集似然函數 profile log-likelihoods {#profile-log-likelihood}


```{r Infer-Session11, child = ('02-Inference/Session11.Rmd')}
```



## Inference Practical 11 {#practical0}

```{r Infer-practical11, child = ('02-Inference/Practical11.Rmd')}
```


# 統計推斷總結 {#summary}


```{r Infer-Session12, child = ('02-Inference/Session12.Rmd')}
```

