# (PART) 統計分析方法 Analytical Techniques {-}

# 探索數據和簡單描述 {#descriptive-stat}

> Happy families are all alike, every unhappy family is unhappy in its own way.
> ~ Leo Tolstoy


> Tidy datasets are all alike, but every messy dataset is messy in its own way.
> ~ Hadley Wickham

```{block2, note-thankTim, type='rmdnote'}
The Analytic Techique lectures were orgainised and taught by Professor [Timothy Collier](https://www.lshtm.ac.uk/aboutus/people/collier.timothy).
```



```{r Analytic-Session01, child = ('03-Analytic-Technique/Session01.Rmd')}
```



# 信賴區間 confidence intervals {#confidence-intervals}



```{r Analytic-Session02, child = ('03-Analytic-Technique/Session02.Rmd')}
```



# 假設檢驗 {#hypo-tests}

```{r Analytic-Session03, child = ('03-Analytic-Technique/Session03.Rmd')}
```


# 相關 association {#association}

```{r Analytic-Session04, child = ('03-Analytic-Technique/Session04.Rmd')}
```



# 比較 Comparisons {#comparisons}

```{r Analytic-Session05, child = ('03-Analytic-Technique/Session05.Rmd')}
```


# 前提和數據轉換 Assumptions and transformations {#assumptions}

```{r Analytic-Session06, child = ('03-Analytic-Technique/Session06.Rmd')}
```
