# (PART) 臨床實驗 Clinical Trials {-}




```{block2, note-thanktimclayton, type='rmdnote'}
The Clinical Trials lectures were organised by [Stuart Pocock](https://en.wikipedia.org/wiki/Stuart_Pocock) and taught by Professor [Tim Clayton](https://www.lshtm.ac.uk/aboutus/people/clayton.tim).
```

# 臨牀實驗的基本原則 {#clinical-trials}

```{r ClinicalTrial-Session01, child = ('05-Clinical-Trials/Session01.Rmd')}

```

## CT practical 01: HRT 與冠心病 {#CT-prac01}

```{r ClinicalTrial-Practical01, child = ('05-Clinical-Trials/Practical01.Rmd')}

```


# 隨機化 Randomisation {#randomisation}

```{r ClinicalTrial-Session02, child = ('05-Clinical-Trials/Session02.Rmd')}

```

## CT practical 02：隨機化練習 Randomisation Practical {#CT-prac02}


```{r ClinicalTrial-Practical02, child = ('05-Clinical-Trials/Practical02.Rmd')}

```


# 試驗結果的報告 Reporting of Trials {#reporting-trials}

```{r ClinicalTrial-Session03, child = ('05-Clinical-Trials/Session03.Rmd')}

```

## CT practical 03：試驗結果報告練習 Reporting Trials Practical {#CT-prac03}

```{r ClinicalTrial-Practical03, child = ('05-Clinical-Trials/Practical03.Rmd')}

```


# 樣本量計算 Sample Size Calculation {#sample-size}

```{r ClinicalTrial-Session04, child = ('05-Clinical-Trials/Session04.Rmd')}

```

## CT practical 04：樣本量計算 {#CT-prac04}

```{r ClinicalTrial-Practical04, child = ('05-Clinical-Trials/Practical04.Rmd')}

```


# 資料監測 Data Monitoring {#data-monitoring}

```{r ClinicalTrial-Session05, child = ('05-Clinical-Trials/Session05.Rmd')}

```

## CT practical 05：資料監測委員會 Data Monitoring Committee {#CT-prac05}

```{r ClinicalTrial-Practical05, child = ('05-Clinical-Trials/Practical05.Rmd')}

```


# 替代性試驗設計 I Alternative Trial Designs I {#alternative-designs-1}

```{r ClinicalTrial-Session06, child = ('05-Clinical-Trials/Session06.Rmd')}

```

## CT practical 06：析因、交叉與群集試驗 Factorial, Crossover and Cluster Trials {#CT-prac06}

```{r ClinicalTrial-Practical06, child = ('05-Clinical-Trials/Practical06.Rmd')}

```


# 替代性試驗設計 II Alternative Trial Designs II {#alternative-designs-2}

```{r ClinicalTrial-Session07, child = ('05-Clinical-Trials/Session07.Rmd')}

```

## CT practical 07：非劣效與等效試驗 Non-Inferiority and Equivalence Trials {#CT-prac07}

```{r ClinicalTrial-Practical07, child = ('05-Clinical-Trials/Practical07.Rmd')}

```


# 多重性 Multiplicity {#multiplicity}

```{r ClinicalTrial-Session08, child = ('05-Clinical-Trials/Session08.Rmd')}

```

## CT practical 08：亞組分析 Subgroup Analysis {#CT-prac08}

```{r ClinicalTrial-Practical08, child = ('05-Clinical-Trials/Practical08.Rmd')}

```


# 試驗方案書撰寫 Protocol Development {#protocol-development}

```{r ClinicalTrial-Session09, child = ('05-Clinical-Trials/Session09.Rmd')}

```


# 系統綜述與 Meta-analysis Systematic Reviews and Meta-analysis {#systematic-reviews-meta-analysis}

```{r ClinicalTrial-Session10, child = ('05-Clinical-Trials/Session10.Rmd')}

```

## CT practical 10：系統綜述與 meta-analysis {#CT-prac10}

```{r ClinicalTrial-Practical10, child = ('05-Clinical-Trials/Practical10.Rmd')}

```


# 使用 ANCOVA 進行基線調整 Baseline Adjustment Using ANCOVA

```{r ClinicalTrial-Session11, child = ('05-Clinical-Trials/Session11.Rmd')}

```

```{r ClinicalTrial-Practical11, child = ('05-Clinical-Trials/Practical11.Rmd')}

```
