# (PART) 貝葉斯統計 Introduction to Bayesian Statistics {-}

# 貝葉斯統計入門 {#intro-Bayes}

> A Bayesian statistician is one who, vaguely expecting a horse and catching a glimpse of a donkey, strongly concludes he has seen a mule.
> ~ Guernsey McPearson's Drug Development Dictionary^[http://www.senns.demon.co.uk/wdict.html]

```{block2, note-thankJavi, type='rmdnote'}
The Introduction to Bayesian Statistics lectures were orgainised and taught by Dr. [F. Javier Rubio](https://sites.google.com/site/fjavierrubio67/) and Professor [Karla DiazOrdaz](https://scholar.google.com/citations?user=GSGcT-EAAAAJ&hl=en).
```

```{r Intro-Bayes-Session01, child = ('08-Intro-to-Bayes/Session01.Rmd')}

```


## Practical Intro-to-Bayes 01

```{r Intro-Bayes-Practical01, child = ('08-Intro-to-Bayes/Practical01.Rmd')}
```




# 貝葉斯定理的應用：單一參數模型 Single-parameter models {#single-para-model}


```{r Intro-Bayes-Session02, child = ('08-Intro-to-Bayes/Session02.Rmd')}

```


## Practical Intro-to-Bayes 02

```{r Intro-Bayes-Practical02, child = ('08-Intro-to-Bayes/Practical02.Rmd')}
```


# 貝葉斯理論在正態分布數據中的應用 Normal distribution applying Bayes' Theorem {#normal-distr}

```{r Intro-Bayes-Session03, child = ('08-Intro-to-Bayes/Session03.Rmd')}

```