# (PART) 貝葉斯統計 Introduction to Bayesian Statistics {-}

# 貝葉斯統計入門 {#intro-Bayes}

> A Bayesian statistician is one who, vaguely expecting a horse and catching a glimpse of a donkey, strongly concludes he has seen a mule.
> ~ Guernsey McPearson's Drug Development Dictionary^[http://www.senns.demon.co.uk/wdict.html]

```{block2, note-thankJavi, type='rmdnote'}
The Introduction to Bayesian Statistics lectures were orgainised and taught by Dr. [F. Javier Rubio](https://sites.google.com/site/fjavierrubio67/) and Professor [Karla DiazOrdaz](https://scholar.google.com/citations?user=GSGcT-EAAAAJ&hl=en).
```

```{r Intro-Bayes-Session01, child = ('08-Intro-to-Bayes/Session01.Rmd')}

```


## Practical Intro-to-Bayes 01

```{r Intro-Bayes-Practical01, child = ('08-Intro-to-Bayes/Practical01.Rmd')}
```




# 貝葉斯定理的應用：單一參數模型 Single-parameter models {#single-para-model}


```{r Intro-Bayes-Session02, child = ('08-Intro-to-Bayes/Session02.Rmd')}

```


## Practical Intro-to-Bayes 02

```{r Intro-Bayes-Practical02, child = ('08-Intro-to-Bayes/Practical02.Rmd')}
```


# 貝葉斯理論在正態分布數據中的應用 Normal distribution applying Bayes' Theorem {#normal-distr}

```{r Intro-Bayes-Session03, child = ('08-Intro-to-Bayes/Session03.Rmd')}

```


# 其他典型的單一參數模型 Other standard single-parameter models

```{r Intro-Bayes-Session04, child = ('08-Intro-to-Bayes/Session04.Rmd')}

```

# 多參數模型 Introduction to multiparameter models 

```{r Intro-Bayes-Session05, child = ('08-Intro-to-Bayes/Session05.Rmd')}

```

# 簡單線型回歸模型 - 地心說模型 Linear regression is the geocentric model of applied statistics

```{r Intro-Bayes-Session06, child = ('08-Intro-to-Bayes/Session06.Rmd')}

```

# 直線和曲線 curves and lines

```{r Intro-Bayes-Session07, child = ('08-Intro-to-Bayes/Session07.Rmd')}

```

# 多重線性回歸模型 many more variables 


```{r Intro-Bayes-Session08, child = ('08-Intro-to-Bayes/Session08.Rmd')}

```

# 有向無環圖 DAG & 可怕的因果 Causal Terror

```{r Intro-Bayes-Session09, child = ('08-Intro-to-Bayes/Session09.Rmd')}

```

# 模型選擇 model selection

```{r Intro-Bayes-Session10, child = ('08-Intro-to-Bayes/Session10.Rmd')}

```

# 交互作用 it's all about interaction

```{r Intro-Bayes-Session11, child = ('08-Intro-to-Bayes/Session11.Rmd')}

```

# 馬可夫鏈蒙地卡羅 MCMC


```{r Intro-Bayes-Session12, child = ('08-Intro-to-Bayes/Session12.Rmd')}

```
 
# 貝葉斯廣義線性回歸 Bayesian GLM

```{r Intro-Bayes-Session13, child = ('08-Intro-to-Bayes/Session13.Rmd')}

```


# 貝葉斯廣義線性回歸模型的擴展 continuous mixture models

```{r Intro-Bayes-Session14, child = ('08-Intro-to-Bayes/Session1401.Rmd')}

```

# 貝葉斯多層回歸模型 multilevel models


```{r Intro-Bayes-Session15, child = ('08-Intro-to-Bayes/Session15.Rmd')}

```