# (PART) 生存分析 Survival Analysis {-}



# 生存分析入門 {#surv-intro}

> The best thing about being a statistician is that you get to play in everyone's backyard.
> ~ John Tukey

```{block2, note-thankRuthAurelien, type='rmdnote'}
The Survival Analysis lectures were orgainised and taught by Professor [Ruth Keogh](https://www.lshtm.ac.uk/aboutus/people/keogh.ruth), and Professor [Aurélien Belot](https://aurelienbelot.netlify.com).
```


## 什麼是生存分析

```{r surv-Session01, child = ('11-Survival/Session01.Rmd')}
```


## Practical Survival 01

```{r surv-Practical01, child = ('11-Survival/Practical01.Rmd')}
```



# 非參數法分析生存數據 {#nonparametric}


```{r surv-Session02, child = ('11-Survival/Session02.Rmd')}
```

## Practical Survival 02

```{r surv-Practical02, child = ('11-Survival/Practical02.Rmd')}

```


# 生存數據中的回歸模型 {#surv-reg}


```{r surv-Session03, child = ('11-Survival/Session03.Rmd')}
```

## Practical Survival 03

```{r surv-Practical03, child = ('11-Survival/Practical03.Rmd')}

```



# Cox 比例風險模型  {#cox}


```{r surv-Session04, child = ('11-Survival/Session04.Rmd')}
```


## Practical Survival 04 

```{r surv-Practical04, child = ('11-Survival/Practical04.Rmd')}

```


# 分析策略和模型檢查 Model checking-survival analysis {#surv-check}

```{r surv-Session05, child = ('11-Survival/Session05.Rmd')}
```


## Practical Survival 05 

```{r surv-Practical05, child = ('11-Survival/Practical05.Rmd')}

```


# 競爭風險模型 competing risk {#competing-risk}

```{r surv-Session06, child = ('11-Survival/Session06.Rmd')}
```


## Practical Survival 06

```{r surv-Practical06, child = ('11-Survival/Practical06.Rmd')}

```


# 生存分析的其他手段 {#other-surv}

```{r surv-Session07, child = ('11-Survival/Session07.Rmd')}
```


## Practical Survival 07 

```{r surv-Practical07, child = ('11-Survival/Practical07.Rmd')}

```


# 時間依存變量 Time-dependent variables 和脆弱模型 frailty model {#time-dep}

```{r surv-Session08, child = ('11-Survival/Session08.Rmd')}
```


## Practical Survival 08 

```{r surv-Practical08, child = ('11-Survival/Practical08.Rmd')}

```




# 時間事件數據的高級分析法 {#surv-advance}


# 貝葉斯生存分析 Bayesian Survival Analysis {#bayes-surv}


