# (PART) 貝葉斯統計學 Bayesian Statistics {-}
	



# 爲什麼我們要用貝葉斯統計學方法？ {#why-bayes}

> Everybody is a Bayesian. It's just that some know it, and some don't. 
> ~ Trivellore Raghunathan

```{block2, note-thankAlex, type='rmdnote'}
Lectures for Bayesian Statistics were orgainised and taught by Professor [Alexina Mason](https://www.lshtm.ac.uk/aboutus/people/mason.alexina) and supported by Dr. [F. Javier Rubio](https://sites.google.com/site/fjavierrubio67/).
```


```{r Bayes-Session01, child = ('12-Bayesian/Session01.Rmd')}
```


# 蒙特卡羅估計和預測 Mente Carlo estimation and prediction {#MC-estimation}


```{r Bayes-Session02, child = ('12-Bayesian/Session02.Rmd')}
```


## Practical Bayesian Statistics 02


```{r Bayes-Practical02, child = ('12-Bayesian/Practical02.Rmd')}

```



# 共軛先驗概率 Conjugate priors {#conjugate-priors}


```{r Bayes-Session03, child = ('12-Bayesian/Session03.Rmd')}
```

## Practical Bayesian Statistics 03 {#BayesPrac03}




```{r Bayes-Practical03, child = ('12-Bayesian/Practical03.Rmd')}

```


# 馬爾可夫鏈蒙特卡羅MCMC，圖形模型，BUGS語言 {#MCMC-methods}

```{r Bayes-Session04, child = ('12-Bayesian/Session04.Rmd')}
```

## Practical Bayesian Statistics 04

```{r Bayes-Practical04, child = ('12-Bayesian/Practical04.Rmd')}

```



# 建模和模型的檢查 {#Bayes-check}

```{r Bayes-Session05, child = ('12-Bayesian/Session05.Rmd')}
```

## Practical Bayesian Statistics 05

```{r Bayes-Practical05, child = ('12-Bayesian/Practical05.Rmd')}

```


# 不同實驗/研究設計時適用的貝葉斯模型 {#Bayes-design}

```{r Bayes-Session06, child = ('12-Bayesian/Session06.Rmd')}
```


## Practical Bayesian Statistics 06

```{r Bayes-Practical06, child = ('12-Bayesian/Practical06.Rmd')}

```


# 貝葉斯廣義線性回歸 {#Bayes-GLM}


```{r Bayes-Session07, child = ('12-Bayesian/Session07.Rmd')}
```


## Practical Bayesian Statistics 07  {#Bayesian-practical07}

```{r Bayes-Practical07, child = ('12-Bayesian/Practical07.Rmd')}

```


# 貝葉斯等級回歸模型 {#Bayes-Hier}


```{r Bayes-Session08, child = ('12-Bayesian/Session08.Rmd')}
```




## Practical Bayesian Statistics 08 


```{r Bayes-Practical08, child = ('12-Bayesian/Practical08.Rmd')}

```



# 再訪 MCMC {#MCMC-revisit}

```{r Bayes-Session09, child = ('12-Bayesian/Session09.Rmd')}
```





# 貝葉斯和概率論的比較  {#compare-Bayes-freq}

> Bayesianisom provides advice about how you should change your degree of belief as you acquire new evidence.

```{r Bayes-Session10, child = ('12-Bayesian/Session10.Rmd')}
```


