
本章練習題會延續使用前一個章節 (Chapter \@ref(Bayesian-practical07)) 中使用的練習題數據，岡比亞兒童使用蚊帳睡眠是否能夠降低或者減輕瘧疾。

1. 把前章練習中的貝葉斯邏輯回歸模型改造成爲一個包含村莊級別隨機效應的多層邏輯回歸模型。


```
# Logistic regression model for malaria data
	
model {
   for(i in 1:149) {
      MALARIA[i] ~ dbin(p[i], POP[i])
      logit(p[i]) <- alpha + beta.age[AGE[i]] +
		                    beta.bednet[BEDNET[i]] + 
						    beta.green*(GREEN[i] - mean(GREEN[])) +
						    beta.phc*PHC[i] + 
							theta[VILLAGE[i]]
   }
   # village-level random effect 
   for (j in 1:25) {
 	   theta[j] ~ dnorm(0, tau)
	   OR.village[j]  <- exp(theta[j])
	   # Odds ratio of malaria in village j relative to the average
   }
  
  
   # vague priors on regression coefficients
   alpha ~ dnorm(0, 0.00001)
   sigma ~ dunif(0, 100)
   tau <- 1/pow(sigma, 2)
   beta.age[1] <- 0        
	   # set coefficient for baseline age group to zero (corner point constraint)
   beta.age[2] ~ dnorm(0, 0.00001)     
   beta.age[3] ~ dnorm(0, 0.00001)     
   beta.age[4] ~ dnorm(0, 0.00001)     
   beta.bednet[1] <- 0    
	   # set coefficient for baseline bednet group to zero (corner point constraint)
   beta.bednet[2] ~ dnorm(0, 0.00001)     
   beta.bednet[3] ~ dnorm(0, 0.00001)     
   beta.green ~ dnorm(0, 0.00001)     
   beta.phc ~ dnorm(0, 0.00001)     
 
   # calculate odds ratios of interest
   OR.age[2] <- exp(beta.age[2]) # OR of malaria for age group 2 vs. age group 1
   OR.age[3] <- exp(beta.age[3]) # OR of malaria for age group 3 vs. age group 1
   OR.age[4] <- exp(beta.age[4]) # OR of malaria for age group 4 vs. age group 1
   
   OR.bednet[2] <- exp(beta.bednet[2]) # OR of malaria for children using untreated bednets vs. not using bednets
   OR.bednet[3] <- exp(beta.bednet[3]) # OR of malaria for children using treated bednets vs. not using bednets
   OR.bednet[4] <- exp(beta.bednet[3] - beta.bednet[2]) # OR of malaria for children using treated bednets vs. using untreated bednets 
   OR.green <- exp(beta.green)  # OR of malaria per unit increase in greenness index of village
   OR.phc <- exp(beta.phc)      # OR of malaria sfor children living in villages belonging to the primary health care system versus children living in villages not in the health care system 
   logit(baseline.prev) <- alpha # baseline prevalence of malaria in baseline group (i.e. child in age group 1, sleeps without bednet, and lives in a village with average greenness index and not in the health care system) 
   
   PP.untreated <- step(1 - OR.bednet[2]) # probability that using untreated bed net vs. no bed net reduces odds of malaria
   PP.treated <- step(1- OR.bednet[4]) # probability that using treated vs. untreated bednet reduces odds of malaria
}
```

```{r BayesianPractical0801, cache=TRUE, fig.width=8, fig.height=20, fig.cap='Density plots for parameters for hierarchical GLM about the odds of malaria regarding netbeds use in Gambia children.', fig.align='center', out.width='80%', message=TRUE, warning=FALSE, echo=TRUE}
# Read in the data: 

Data <- read_delim(paste(bugpath, "/backupfiles/malaria-data.txt", sep = ""), delim = " ")

# Data file for the model
Dat <- list(
  POP = Data$POP, 
  MALARIA = Data$MALARIA, 
  AGE = Data$AGE, 
  BEDNET = Data$BEDNET,
  GREEN = Data$GREEN,
  PHC = Data$PHC,
  VILLAGE = Data$VILLAGE
)


# initial values for the model
# the choice is arbitrary

inits <- list(
 list(alpha = -0.51, 
      beta.age = c(NA, 0.83,  0.28, -1.68), 
      beta.bednet = c(NA, -2.41,  0.68), 
      beta.green = -0.23, 
      beta.phc = 1.82,
      sigma = 3), 
initlist1 <- list(alpha = 1.29, 
                  beta.age = c(NA, 0.49, -0.38, -0.04),  
                  beta.bednet = c(NA, 6.85,  0.09), 
                  beta.green = 2.66, 
                  beta.phc = -0.31,
                  sigma = 1)
)



# Set monitors on nodes of interest
parameters <- c("OR.age", "OR.bednet", "OR.green", "OR.phc", "PP.treated", "PP.untreated", "baseline.prev", "sigma", "OR.village")

# fit the model in jags
jagsModel <- jags(data = Dat,
                  model.file = paste(bugpath, 
                                  "/backupfiles/malaria-model-hierarchical.txt",
                                  sep = ""),
                    parameters.to.save = parameters,
                     n.iter = 1000,
                     n.chains = 2, 
                     inits = inits,
                     n.burnin = 0,
                     n.thin = 1,
                    progress.bar = "none")

# Show the trace plot
Simulated <- coda::as.mcmc(jagsModel)
ggSample <- ggs(Simulated)
ggSample %>% 
  filter(Parameter %in% c("OR.age[2]", "OR.age[3]", "OR.age[4]", 
                          "OR.bednet[2]", "OR.bednet[3]", "OR.bednet[4]",
                          "OR.green", "baseline.prev", "OR.phc", "OR.village[1]")) %>% 
  ggs_traceplot()
```




```{r BayesianPractical0802, cache=TRUE, fig.width=15, fig.height=8, fig.cap='Gelman-Rubin convergence statistic of parameters for GLM about the odds of malaria regarding netbeds use in Gambia children.', fig.align='center', out.width='80%', message=FALSE, warning=FALSE, echo=FALSE}
gelman.diag(Simulated)
gelman.plot(Simulated)
```


基本可以認爲刨除前1000次取樣 (burn-in) 可以達到收斂。



```{r BayesianPractical0803, cache=TRUE, message=TRUE, echo=TRUE}

jagsModel <- jags(data = Dat,
                  model.file = paste(bugpath, 
                                  "/backupfiles/malaria-model-hierarchical.txt",
                                  sep = ""),
                    parameters.to.save = parameters,
                     n.iter = 26000,
                     n.chains = 2, 
                     inits = inits,
                     n.burnin = 1000,
                     n.thin = 1,
                    progress.bar = "none")
print(jagsModel)
```

從多層邏輯回歸分析的結果來看，每個變量的事後概率分佈的標準差都比無考慮村莊這一隨機效應時要大一些。這主要是因爲，多層回歸模型考慮了數據中村莊這個層面的過度離散效應(overdispersion)。但是整體的來說，每個比值比的含義並沒有發生太多改變。另外，村莊層級的隨機效應，其方差的事後均值爲 `0.915`，這是相對高的過度離散效應的表現。DIC結果也比無隨機效應的邏輯回歸模型提升顯著 `476.8->396.8`。這也是村莊層級隨機效應十分顯著的證據之一。
